Bird beak's elaboration and innovation

### 2022-06-14 Analysis/10-sensitivity_analysis.Rmd
Update 10-sensitivity_analysis.Rmd

Model | parameters | replicates | trees sampled | spaces sampled | posterior VCVs |
------|------------|------------|---------------|----------------|----------------|
shapespace | from shapespace | 100 | 1 | 1000
randomspace | from shapespace | 100 | 25 | 1000
BMspace | from shapespace | 100 | 25 | 1000
ballspace | from ballspace | 100 | 1 | 1000

>>>>

Model       | parameters      | replicates | trees sampled | spaces sampled | posterior VCVs |
------------|-----------------|------------|---------------|----------------|----------------|
shapespace  | from shapespace | 100        | 100           | 1              | 1000
randomspace | from shapespace | 100        | 100           | 25             | 1000
BMspace     | from shapespace | 100        | 100           | 25             | 1000
ballspace   | from ballspace  | 100        | 100           | 1              | 1000
